This is the Title

### 2017-03-04 trunk/abc/paper/paper.tex
Some notes, etc. from RIVERCITY
Attempted to write some authoritative description of the layout strategy and calling convention; add 32-bit literals since those will be easy
Make more of the EXE filler be printable. Break out X86 encoding and functorize it as per the perfomance TODO. This helped tremendously--9x the speed with mlton
Fix bugs and add some 16-bit addressing modes (note possible large code size improvement from using these for temp addressing, etc.). builtin and simpcall tests both work, whee

>>>>

% Literate executable, knuth
% In the dead space of the binary, put this paper or part of it

% ``PISC'' = Printable Instruction Set Computer, etc.

It's a common experience that each time you program a solution to a
hard problem, you do it a different way, due to a lack of complete
satisfaction with the way you did it last time. True to form, the
ABC compiler exercises this technique *within the same compiler*,
using a different approach to represent each of the intermediate
languages.

Thank you for playing wing commander.

TODO: Convert byte table thing into ascii. Unfortunately can't fit
the whole 256x256 thing, so maybe 128x128 with a small amount of
cropping, then a 1:1 zoom on the sierpinski triangle part?

this page confirms the wrap-around with jumps btw:
http://www.felixcloutier.com/x86/Jcc.html
(Probably already in the x86 manual actually?)

Another possibility is to include readable debug information (e.g.
frame layouts) in a separate section.

BTW here is eicar:

X5O!P%@AP[4\PZX54(P^)7CC)7}$EICAR-STANDARD-ANTIVIRUS-TEST-FILE!$H+H*

It does indeed use self-modifying code to create the interrupt
instructions, which it uses to print the string and exit.

histogram of actual bytes used in code segment?

interesting bugs:
  DI <- [DI]
